Simulation Tables

### 2019-06-14 manuscript/manuscript.tex
simulation changes

$$\mathbf{Y}_{n_k \times J} \sim \mathcal{MATSN}_{n_k \times J}(\mathbf{M},\boldsymbol\alpha_k,\mathbf{I}_{n_k},\boldsymbol\Sigma_k)$$

$$\text{vec}(Y) = \mathbf{y}_{n_kJ \times 1} = (\mathbf{y}^T_1,...,\mathbf{y}^T_{n_k})$$

@@

where $\mathbf{w}_i$ is the vector of class probability covariates for subject $i$, $\boldsymbol\delta_k$ contains the multinomial regression parameters for class $k$, and $K$ is the number of putative clusters specified \textit{a priori}. For identifiability purposes, we fix the reference category $k = K$ and set $\boldsymbol\delta_K = \mathbf{0}$.

\[   P(Z_i = k|\mathbf{w}_i,\boldsymbol\delta_k) = \left \{
\begin{array}{ll}
      \pi_{ik} = \frac{e^{\mathbf{w}_i^T \boldsymbol\delta_k}}{1 + \sum_{k' = 1}^{K-1} e^{\mathbf{w}_i^T \boldsymbol\delta_{k'}}} & k < K \\
      \\
      \pi_{ik} = \frac{1}{1 + \sum_{k' = 1}^{K-1} e^{\mathbf{w}_i^T \boldsymbol\delta_{k'}}} & k = K \\
\end{array} 
\right. \]

\

Under this model, $Z_i|\mathbf{w}_i \sim Multinom.(1,\boldsymbol\pi_i)$, where $\boldsymbol\pi_i = (\pi_{i1},...,\pi_{1K})$

During MCMC estimation, the class labels $z_i$ are updated from their multinomial full conditional distribution and used in the remaining MCMC steps as class assignments.

>>>>

$$\mathbf{Y}_{n_k \times J} \sim \mathcal{MATSN}_{n_k \times J}(\mathbf{M},\boldsymbol\alpha_k,\mathbf{I}_{n_k},\boldsymbol\Sigma_k)$$
$$\text{vec}(\mathbf{Y}) = \mathbf{y}_{n_kJ \times 1} = (\mathbf{y}^T_1,...,\mathbf{y}^T_{n_k})$$
$$\text{vec}(\mathbf{M}) = \boldsymbol\mu_{n_k J \times 1} = (\boldsymbol\mu_1^T,...,\boldsymbol\mu_{n_k}^T)$$

where $\boldsymbol\mu_i = \mathbf{x}_i \boldsymbol\beta_k$ and $\boldsymbol\alpha_k = (\alpha_{k1},...,\alpha{kJ})$. This implies that the $i^{th}$ row of $\mathbf{Y}$ is $\mathbf{y}_i \sim \mathcal{MSN}_J(\boldsymbol\mu_i, \boldsymbol\alpha_k, \boldsymbol\Sigma_{J \times J}) = \mathcal{MSN}_J(\mathbf{x}_i \boldsymbol\beta_k, \boldsymbol\alpha_k, \boldsymbol\Sigma)$. Using the stochastic representation presented in Section 3.2, the conditional distribution $\mathbf{y}_i | Z_i, t_i \sim N_J (\mathbf{x}_i \boldsymbol\beta_k + \boldsymbol\psi_k t_i,\boldsymbol\Sigma_k)$. This implies that all responses for cluster $k$ conditioned on $\mathbf{T}_{n_k \times 1}$ is distributed as

$$\mathbf{Y}_{n_k \times J} | \mathbf{T} = \mathbf{t} \sim N_{n_k \times J}(\mathbf{M}_k, \mathbf{I}_{n_k}, \boldsymbol\Sigma_k)$$
$$\text{vec}(\mathbf{M}_k)_{n_kJ \times 1} = \mathbf{X}_{k} \boldsymbol\beta_k + \mathbf{t}_k \otimes \boldsymbol\psi_k$$\

where $\mathbf{t}_k = (t_1,...,t_{n_k})$.

@@

where $\mathbf{w}_i$ is the vector of class probability covariates for subject $i$, $\boldsymbol\delta_k$ contains the multinomial regression parameters for class $k$, and $K$ is the number of putative clusters specified \textit{a priori}. For identifiability purposes, we fix the reference category $k = K$ and set $\boldsymbol\delta_K = \mathbf{0}$. Under this model, $Z_i|\mathbf{w}_i \sim Multinom.(1,\boldsymbol\pi_i)$, where $\boldsymbol\pi_i = (\pi_{i1},...,\pi_{1K})$. During MCMC estimation, the class labels $z_i$ are updated from their multinomial full conditional distribution and used in the remaining MCMC steps as class assignments.

### 2019-06-14 mcmc_draws_2019-06-13/tables.Rmd
simulation changes

model_component <- c("MVSN","Regression","","","","","","","",
                     "Multinom.","",
                     "Clustering")
params <- c("$\\beta_{0}$","$\\beta_{1}$","$\\beta_{2}$","$\\beta_{3}$",
            "$\\sigma_{11}$","$\\sigma_{12}$",
            "$\\sigma_{22}$",
            "$\\psi_{1}$","$\\psi_{2}$",
            "$\\delta_{11}$","$\\delta_{12}$",
            "$\\pi_l$")

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1500, k = 2, p = 2, h = 3, v = 1. 5000 iterations were run with a burn in of 1000. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,4) %>%
  group_rows(" ",5,7) %>%
  group_rows(" ",8,10) %>%
  group_rows(" ",10,10) %>%
  group_rows(" ",12,12)
```

>>>>

model_component <- c("MVSN","Regression","","","","","","","","","","","","","","","","",
                     "Multinom.","",
                     "Clustering")
params <- c("$\\beta_{0}$","$\\beta_{1}$","$\\beta_{2}$","$\\beta_{3}$",
            "$\\sigma_{11}$","$\\sigma_{12}$","$\\sigma_{13}$","$\\sigma_{14}$",
            "$\\sigma_{22}$","$\\sigma_{23}$","$\\sigma_{24}$",
            "$\\sigma_{33}$","$\\sigma_{34}$",
            "$\\sigma_{44}$",
            "$\\psi_{1}$","$\\psi_{2}$", "$\\psi_{3}$","$\\psi_{4}$",
            "$\\delta_{11}$","$\\delta_{12}$",
            "$\\pi_l$")

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1500, k = 4, p = 1, h = 3, v = 1. 5000 iterations were run with a burn in of 1000. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,4) %>%
  group_rows(" ",5,14) %>%
  group_rows(" ",15,18) %>%
  group_rows(" ",19,20) %>%
  group_rows(" ",21,21)
```
